How to compute the fusion product of MV cycles in type A

### 2021-02-16 draft.tex
updated bib

In Anderson and Kogan conjectured in \cite{anderson2005algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
and they conjecture a formula for many of them.

@@

$x*y=\sum z\Rightarrow y = \frac 1 x \sum z$.

>>>>

In Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
and they conjecture a formula for many of them.

@@

% No; $x*y=\sum z\Rightarrow y = \frac 1 x \sum z$.
